---
title: "R Markdown PowerPoint Demo"
author: "Josh Radack"
date: "Last rendered on `r Sys.Date()`"
output:
  powerpoint_presentation:
    toc: true # Creates a table of contents slide
    reference_doc: ../inputs/reference-ppt.pptx # This specifies the custom template file
---

```{r, setup, include=FALSE}
# This code chunk is used to set up global options for the R Markdown document
knitr::opts_chunk$set(echo = FALSE)

# It's a good place to load packages too
library(tidyverse)
library(flextable)
```


# New Section

## Slide Title

::: incremental

- I can make a bulleted list
- Where the bullet points appear incrementally
  - Here's a sub-item
  - Make sure to indent!
- Some more bullet points
- Inlcuded here

:::

## Tables and New Slides

- Let's create a table using the `mtcars` dataset
- Two different methods
  - Markdown syntax
  - Directly printing a `data.frame` with `flextable`

---

| Statistic | Value |
|-----------|-------|
| Minimum | `r min(mtcars$mpg)` |
| Q1 | `r quantile(mtcars$mpg, 0.25)` |
| Median | `r median(mtcars$mpg)` |
| Q3 | `r quantile(mtcars$mpg, 0.75)` |
| Maximum | `r max(mtcars$mpg)` |


---

```{r, five-number-summary}
set_flextable_defaults(
  font.size = 10,
  theme_fun = theme_vanilla,
  padding = 6,
  background.color = "#EFEFEF"
)

mtcars %>%
  summarize(
    Minimum = min(mpg),
    Q1 = quantile(mpg, 0.25),
    Median = median(mpg),
    Q3 = quantile(mpg, 0.75),
    Maximum = max(mpg)
  ) %>%
  pivot_longer(
    everything(),
    names_to = "Statistic",
    values_to = "Value"
  ) %>%
  flextable() %>%
  autofit()
```

## A slide with text and a figure

- Embedding R code into a slide
- Generate tables and plots
- Display them on a slide

```{r, density-plot, message = FALSE}
# Set up seed and parameters
set.seed(100)
pop_mean = 5
pop_sd = 5

# Generate random sample
df <- data.frame(
  x = rnorm(1000, mean = pop_mean, sd = pop_sd)
)

# Plot the results
df %>%
  ggplot(aes(x = x)) +
  geom_histogram(
    aes(y = after_stat(density))
  ) +
  geom_function(
    fun = dnorm,
    args = list(mean = pop_mean, sd = pop_sd),
    color = "red"
  )
```

## Multi-Column Slide

:::::: {.columns}
::: {.column}
- Content of the left column.
- Some more stuff
- *Markdown* syntax can be **utilized**
:::

::: {.column}
- Content of the right column.
- Some other stuff
:::
::::::

